\documentclass[MTRX3700report.tex]{subfiles}
% Dpak
% HARDWARE DESIGN
\begin{document}

Give a detailed description of the design of hardware. The description should include mechanical drawings, location diagrams, electrical circuit schematics, circuit simulation or test results, PCB overlays, wiring diagrams, connector pinout lists, pneumatic/hydraulic circuit diagrams

\subsection{Scope of the Something System Hardware}
Statement of what is, and what is not, being designed and described here.
\subsection{Hardware Design}
\subsubsection{Power Supply}
Power supply method and rating, fusing, distribution, grounding and protective earth as appropriate.
\subsubsection{Computer Design}
Description of computer hardware, including all interface circuitry to sensors, actuators, and I/O hardware.
\subsubsection{Sensor Hardware}
\subsubsection{Actuator Hardware}
\subsubsection{Operator Input Hardware}
\subsubsection{Operator Output Hardware}
\subsubsection{Hardware Quality Assurance}
Describe any measures that were taken to control (improve) hardware quality and reliability – Heartbeats, brownout conditioning/resets, reset conditions, testing and validation, etc.

\subsection{Hardware Validation}
Details of any systematic testing to ensure that the hardware actually functions as intended.
\subsection{Hardware Calibration Procedures}
Procedures for calibration required in the factory, or in the field.
\subsection{Hardware Maintenance and Adjustment}
Routine adjustment and maintenance procedures.


\end{document}