\documentclass[MTRX3700report.tex]{subfiles}


\begin{document}
<<<<<<< HEAD
%\section{Introduction}
\subsection{Document Identification}
  This document describes the design of a remote controlled robot system, that took part in a jousting tournament for the subject MTRX3700 - Mechatronics 3, at the University of Sydney. The tournament took place in October 2015, and this document describes the system implemented by the House of Faintree.
\subsection{System Overview}
  The robotic system was designed to take part in a jousting tournament and as such consisted of wireless communication between 2 modules allowing for remote control of the robotic system. The controller in the hands of the end-user is referred to in this document as the Commander, and it provides control over the Mobile Robot system. The Mobile Robot also has a limited intelligence to allow it to function autonomously in the tournament without direct instructions from the Commander when allowed to do so.
\subsection{Document Overview}
  \textit{A short “road map” of the document, to provide an orientation for the reader. Summarise the purpose and contents of this document.}
  \begin{description}
    \item[Section 2:]
      This document will begin in Section 2 by giving a description of the system from a high level perspective, including design choices that were made due to the operational scenarios the robot was meant to be in. This section will give an overview of the individual modules from a design perspective.
    \item[Section 3:]
      will guide the reader through the user interface design - what inputs and outputs are available to the end-user, how those interfaces were arrived at, and how they have changed over the course of the project.
    \item[Section 4:]
      relates to the low level Hardware design choices made in the project, with explanations on how individual hardware components function, what calibration if any was required, and generally will provide the means to reconstruct the project if needed, without any explanation of software interfaces to the hardware.
    \item[Section 5:]
      will guide the reader through the Software Design process that took place to meet the requirements of the project and will include the high level software architecture, internal workings of software components and the public interfaces made available for other components to utilize.
    \item[Section 6:]
      expands on the performance testing done on the robotic system to evaluate characteristics such as reliability, accuracy and adherence to he project outlines introduced in the design process. The final state of the product as delivered is stated, with future improvements that could be made outlined that were arrived at during the process of design, construction, and implementation.
    \item[Section 7:]
      since the robotic system constructed for the project is mobile and fairly heavy, there is a significant risk factor associated with the operation of the system, compounded by the fact that the Mobile Robot was given some agency to decide its own movements in autonomous mode. This section seeks to outline some of the health hazards presented by this system, and also some solutions to minimize risks.
    \item[Section 8:]
      this document will end on some concluding remarks such as lessons learned and possible extensions or applications of the project into other applications.
    \end{description}

\subsection{Reference Documents}
  The present document is prepared on the basis of the following reference documents, and should be read in conjunction with them.\\
  —.  “CAN Specification 2.0”.  Robert Bosch GmbH, Stuttgart, September 1991.\\
  —.  “OMG Unified Modeling Language Specification”, vers.1.3, June 1999.

\subsubsection{Acronyms and Abbreviations}
  Table \ref{Acro} lists the acronyms and abbreviations used in this document.
  \begin{table}[h]
  \centering
  \caption{Acronyms and Abbreviations}
  \label{Acro}
  \begin{tabular}{|l|l|}
  \hline Acronym & Meaning \\
  \hline MPC & Model Predictive Control \\
  \hline & \\
  \hline
  \end{tabular}
  \end{table}
=======
\section{Introduction}
This section is intended to give a general overview of the basis for the Robotic System design, and introduce each module in hardware and software.
\subsection{Document Identification}
This document describes the design of Robotic System for Jousting. This document is prepared by Group Leo Lou for assessment in MTRX3700 in 2015.
\subsection{System Overview}
The Robotic System is a system that can be controlled by the user or it can run in a fully automatic mode. Through the Xbee, the motor driver board (Pololu 707), power board, the PWM motor, encoder and joysticks that controlled by the user. The robotic system (which is a mobile robot) can be operated in manual mode, auto assist mode and automatic mode. In addition, the status of the robotic can be displayed on a LCD screen

\subsection{Document Overview}  

Part 1 of this document is an introduction of the report.\\
Part 2 part of the report demonstrate the system overview and its expect performance. What its interface will be look like and show the design procedure.\\
Part 3 of the document describe the user interface design and show how the system will be handle the error input.\\
Part 4 describe the hardware components, the actuators, sensors and controller. It also point out how they can be integrated together.\\
Part 5 describe the software components of the robotic and controller system. The flow chart and data blocked will be explained. The robot motion algorism, serial communication (Xbee).\\ controller algorism and robot mode will be shown. Other parts such as LCD user interface will be explained.\\
Part 6 describe the testing procedure. It will explain how individual component will be test and demo it to the group member.\\


\subsection{Reference Documents}
The present document is prepared on the basis of the following reference documents, and should be read in conjunction with them.\\
\begin {itemize}
	\item  MICROCHIP PIC18FXX2 Data Sheet
	\item  PIC18F452 to PIC18F4520 Migration Guide
	\item Xbee manual.
	\item Manual and circuit schematic for MNML*PIC*18 v2
	\item STVHN3SP30 Infrared sensor Data Sheet
	\item Power Board Design Notes and Manual.

\end{itemize}

\subsubsection{ Acronyms and Abbreviations}
Table   1-1 lists the acronyms and abbreviations used in this document.\\
Acronyms and Abbreviations.
\begin{center}
	\begin{tabular}{| l | l | }
	\hline
	Acronyms & Abbreviations		\\ \hline
	PWM	& Pulse Width Modulation	\\ \hline	
	ISR    & Interrupt service routine \\ \hline
	ADC  & Analog Digital Converter   \\ \hline
	Xbee & Radio communication	\\ 
	\hline
	\end{tabular}
\end{center}
	


		
	


>>>>>>> origin/master


\end{document}
